Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-11 documentation/paper.tex
Switched out graphs to highlight particle types rather than run types

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{grav_opt_validation}
    \caption{\label{grav_opt_validation} Accuracy of best gravitational differentiation training run compared to Acoustic Parameter (98\% accuracy).}
\end{figure}

@@

During a grid search of parameters of the gravitational differentiation algorithm (in addition to the stochastic gradient descent learning rate), the algorithm achieved a maximum of 98\% validation accuracy. The mean over that run (also the highest overall) was 96\%. Figure \ref{grav_opt_validation} shows the highly accurate replication of Acoustic Parameter.

@@

>>>>

@@

During a grid search of parameters of the gravitational differentiation algorithm (in addition to the stochastic gradient descent learning rate), the algorithm achieved a maximum of 98\% validation accuracy. The mean over that run (also the highest overall) was 96\%. Figure \ref{grav_grid_search} shows the highly accurate replication of Acoustic Parameter.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{grav_grid_search}
    \caption{\label{grav_grid_search} Accuracy of best gravitational differentiation training run compared to Acoustic Parameter (98\% accuracy).}
\end{figure}
